---
title: "MLR_nwins"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(GGally)
library(modelr)
library(hexbin)
library(jsonlite)
library(httr)
library(patchwork)
library(plotly)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Section Introduction

To enter the playoff season, New York Knicks needs to win enough games in regular season to rank top 8 in the east. So in this section, we are going to explore the distribution of the number of winnings by the 8th teams in the last 20 years in both west and east conference. We call the number of games won by the 8th in regular season as threshold since it is the least qualification for playoff. Then, as the thresholds are independent each year, we want to use the average performance of a team in regular season to predict it.

## Data Wrangling

As we are about to predicting the number of wins using the average performance of a team, datasets including both the offensive level and defensive level are needed. 

### Box Score dataset

Read the box_score dataset.
```{r,message=FALSE, warning=FALSE}
box_score_all = read_csv("./data2/box_score_all.csv") %>% 
  janitor::clean_names() %>% 
  select(-contains("rank"))
```

The box_score_all dataset contains statistics in individual games. Totally `r nrow(box_score_all)` games' statistics from season 2012-2013 to season 2020-2021 were documented, which includes `r ncol(box_score_all)` variables. We are going to use some of them in the following exploratory data analysis.

### Other dataset

```{r}
box_score_all = read_csv("./data2/box_score_all.csv") %>% 
  janitor::clean_names() %>% 
  select(-contains("rank"))

pass_df = 
  read_csv("./data2/pass_df.csv") %>% 
  select(season_year, team_abbreviation, passes_made)

isol_df = 
  read_csv("./data2/isol_df.csv") %>% 
  select(season_year, team_abbreviation, poss) %>% 
  rename(poss_iso = poss)

prbh_df = 
  read_csv("./data2/prbh_df.csv") %>% 
  select(season_year, team_abbreviation, poss) %>% 
  rename(poss_prb = poss)

prrm_df = 
  read_csv("./data2/prrm_df.csv") %>% 
  select(season_year, team_abbreviation, poss) %>% 
  rename(poss_prr = poss)

defend_df = 
  read_csv("./data2/defensive_impact_df.csv") %>% 
  select(season_year, team_abbreviation, stl, blk, dreb)

trans_df = 
  read_csv("./data2/transition_df.csv") %>% 
  select(season_year, team_abbreviation, poss) %>% 
  rename(poss_trans = poss)
```

* isolation_df: average isolation by team and season
* transition_df: average transition by team and season
* passing_df: average of passes each game
* defensive_impact_df: contain **defensive** variables
* pick_roll_baller_df: average pick and roll for ball handler by team and season
* pick_roll_roller_df: average pick and roll for roll man by team and season

### Huge wrangling to get avg_df, predict_df

```{r,message=FALSE, warning=FALSE}
avg_df = 
  box_score_all %>% 
  select(season_year, team_abbreviation, wl, pts, ast, tov, fgm, fga, fg3m, fg3a) %>%
  mutate(
    win = case_when(wl == "W" ~ 1, TRUE~0),
    game_num = 1,
    fg3a_p = round(fg3a/fga, digits = 3),
    team_abbreviation = str_replace(team_abbreviation, "NOH", "NOP"), 
    team_abbreviation = str_replace(team_abbreviation, "NJN", "BKN"),
    conference = case_when(
      team_abbreviation %in% c("UTA","PHX","LAC","DEN","DAL","LAL","POR","GSW","SAS","MEM","NOP","SAC","MIN","OKC","HOU","SEA","NOK","CHH")~"west",
      team_abbreviation %in% c("PHI","BKN","MIL","ATL","NYK","MIA","BOS","IND","WAS","CHI","TOR","CLE","ORL","DET","CHA")~"east") # divide into east and west conference
    ) %>% 
  group_by(season_year, team_abbreviation, conference) %>% 
  summarise(
    wins = sum(win), 
    games = sum(game_num), 
    games_should = 82, 
    pts_avg = round(mean(pts), digits = 1), 
    ast_avg = round(mean(ast), digits = 1),
    tov_avg = round(mean(tov), digits = 1),
    fgm_total = sum(fgm), 
    fga_total = sum(fga), 
    fg3m_total = sum(fg3m), 
    fg3a_total = sum(fg3a)
    ) %>% 
  mutate(wins_revised = round(wins/games*games_should,0)) %>% # due to labor negotiation in 2011-12, COVID-19.
  relocate(season_year, team_abbreviation, conference, wins, wins_revised, everything()) %>% 
  arrange(desc(season_year),desc(wins)) %>% 
  mutate(fg3_p = fg3a_total/fga_total, fg3_r = fg3m_total/fg3a_total) %>% 
  group_by(season_year,conference) %>% 
  mutate(
    conf_rank = row_number(),
    play_off_team = case_when(
           conf_rank <= 8 ~ "playoff", 
           conf_rank > 8 ~ "non-playoff"
         ), 
         play_off_team = fct_relevel(play_off_team, c("playoff", "non-playoff")))
```

```{r,message=FALSE, warning=FALSE}
predict_df = 
  avg_df %>%
  left_join(defend_df, by = c("season_year","team_abbreviation")) %>% 
  left_join(prrm_df, by = c("season_year","team_abbreviation")) %>% 
  left_join(prbh_df, by = c("season_year","team_abbreviation")) %>%
  left_join(isol_df, by = c("season_year","team_abbreviation")) %>% 
  left_join(pass_df, by = c("season_year","team_abbreviation")) %>%
  left_join(trans_df, by = c("season_year","team_abbreviation")) %>% 
  drop_na(poss_trans, passes_made, poss_iso, poss_prb, poss_prr, stl, blk, dreb) %>% 
  mutate(
    poss_pr = poss_prr + poss_prb
  ) %>% 
  select(-poss_prr, -poss_prb, -wins, -games, -games_should, -fgm_total, -fga_total)
```

Data wrangling process:

1).select the variables we are interested from box_score_all.

2).define four new variables. 
* `win`: 1 means winning and 0 means lost.
* `game_num`: constant 1 used to sum the number of games.
* `fg3a_p`: the percentage of 3 point field goal attempt.
* `conference`: west or east

3).exploratory data analysis.
* calculate total number of wins, total number of games, total number of field goal attempt, total number of field goal made, total number of 3 points field goal attempt and total number of 3 points field goal made by team and season.
* calculate average number of points, average number of assists and average number of turnovers by team and season.
* revised the number of wins in strike season and COVID-19 season.
* locate key variables at the first.
* arrange all data by season year and number of wins.


### Variable description

Dependent variable is the number of wins by team and season, denoted by wins_revised.

Independent variables are selected from both offensive aspect and defensive part.

The typical attributes of "small ball era" is more three points shooting and quicker speed. So we select the following variables representing offensive level of a team:
* fg3_p: proportion of three points shooting
* fg3_r: three points shooting rate
* pts_avg: average points per game
* tov_avg: average number of turnovers per game
* ast_avg: average number of assists per game
* poss_trans: average number of transitions
* passes_made: average number of passes per game
* poss_iso: average number of isolations per game 
* poss_pr: average number of pick and rolls

As for the defensive level, variables include:

* stl: average steals per game
* blk: average blocks per game
* dreb: average defensive rebounds per game

## EDA

### Find the distribution of "threshold"

Recall “threshold”: the number of games won by the 8th team in both west and east conference.

Plot the threshold over last 20 years.
```{r,message=FALSE, warning=FALSE}
eighth_wins =
  avg_df %>% 
  filter(conf_rank == 8)


ggplot(data = eighth_wins,aes(x = wins_revised)) + 
  geom_bar() + 
  theme_bw() 
```

```{r}
summary(eighth_wins$wins_revised)
```

There are `r nrow(eighth_wins)` observations of threshold in the past 20 years, which follows a normal distribution with mean `r mean(eighth_wins$wins_revised)` and variance `r var(eighth_wins$wins_revised)`. The upper limit of 95% confidence interval is `r mean(eighth_wins$wins_revised)+qt(0.975,39)*sd(eighth_wins$wins_revised)/39^0.5`. If the number of wins of new york knicks this season can reach this level, we are highly confident that they will enter the playoff.

Then we are going to deep dive the factors associated with the number of wins per season for a team and try to find significant contributors to increase the number of wins. 

### EDA on average performance

Is there any difference in three field goal percent, scores, block, steal, turnover, passing between regular season team and playoff season team in each game?
```{r, warning=FALSE}
box_score_viz = 
  box_score_all %>% 
  filter(season_year %in% c("2011-12", "2012-13", "2013-14", "2014-15", "2015-16", "2016-17", "2017-18", "2018-19", "2019-20", "2020-21")) %>% 
  mutate(team_abbreviation = str_replace(team_abbreviation, "NOH", "NOP"), 
    team_abbreviation = str_replace(team_abbreviation, "NJN", "BKN")) %>% 
  select(season_year, team_abbreviation, wl, pts, ast, tov, fgm, fga, fg3m, fg3a, stl, blk, dreb) %>%
  mutate(
    win = case_when(wl == "W" ~ 1, TRUE~0),
    game_num = 1, 
    conference = case_when(
      team_abbreviation %in% c("UTA","PHX","LAC","DEN","DAL","LAL","POR","GSW","SAS","MEM","NOP","SAC","MIN","OKC","HOU","SEA","NOK","CHH")~"west",
      team_abbreviation %in% c("PHI","BKN","MIL","ATL","NYK","MIA","BOS","IND","WAS","CHI","TOR","CLE","ORL","DET","CHA")~"east"), # divide into east and west conference
    fg3a_p = round(fg3a/fga, digits = 3),
    fg3_r = round(fg3m/fg3a, digits = 3)
    ) %>% 
  relocate(season_year, team_abbreviation, conference)

conf_rank = 
  avg_df %>% 
  filter(season_year %in% c("2011-12", "2012-13", "2013-14", "2014-15", "2015-16", "2016-17", "2017-18", "2018-19", "2019-20", "2020-21")) %>% 
  ungroup() %>% 
  select(season_year, team_abbreviation, conference, conf_rank)


#join the two table together
box_score_viz = 
  box_score_viz %>% 
  left_join(conf_rank, by = c("season_year", "team_abbreviation", "conference")) %>% 
  mutate(play_off_team = case_when(
           conf_rank <= 8 ~ "playoff", 
           conf_rank > 8 ~ "non-playoff"
         ), 
         play_off_team = fct_relevel(play_off_team, c("playoff", "non-playoff")), 
         fg3p = fg3m / fg3a) %>% 
  relocate(season_year, team_abbreviation, conference, play_off_team)
```

1. Three pointer rate in each play - playoff season team vs. regular season team
playoff season teams have a higher three pointer rate compared to regular season team
```{r}
box_score_viz %>% 
  ggplot(aes(x = season_year, y = fg3p, fill = play_off_team)) + 
  geom_boxplot(alpha = .6)

plot_ly(box_score_viz, x = ~ season_year, y = ~ fg3p, color = ~ play_off_team, type = "box") %>% 
  layout(boxmode = "group", 
         xaxis = list(title = 'Season Year'),
         yaxis = list(title = "Three Pointer Rate"))
```

2. Three pointer attempt in each play - play off season team vs. regular season team
playoff season team have more three field goal attempt during a game. On the other hand, we can see that three field attempts was increasing in game in the last 10 seasons.
```{r}
plot_ly(box_score_viz, x = ~ season_year, y = ~ fg3a, color = ~ play_off_team, type = "box") %>% 
  layout(boxmode = "group", 
         xaxis = list(title = 'Season Year'),
         yaxis = list(title = "Three Point Attempt"))
```


3. steal
There is no obvious pattern in steal data when comparing playoff season team and regular season team
```{r}
plot_ly(box_score_viz, x = ~ season_year, y = ~ stl, color = ~ play_off_team, type = "box") %>% 
  layout(boxmode = "group", 
         xaxis = list(title = 'Season Year'),
         yaxis = list(title = "Steal"))
```

4. Block
There is no significant difference in the block data between playoff season team and regular season team
```{r}
plot_ly(box_score_viz, x = ~ season_year, y = ~ blk, color = ~ play_off_team, type = "box") %>% 
  layout(boxmode = "group", 
         xaxis = list(title = 'Season Year'),
         yaxis = list(title = "Block"))
```

5. Turnover
```{r}
plot_ly(box_score_viz, x = ~ season_year, y = ~ blk, color = ~ play_off_team, type = "box") %>% 
  layout(boxmode = "group", 
         xaxis = list(title = 'Season Year'),
         yaxis = list(title = "Block"))
```

6. Defensive Rebounds
Playoff teams have more defensive rebounds than non-playoff teams
```{r}
plot_ly(box_score_viz, x = ~ season_year, y = ~ dreb, color = ~ play_off_team, type = "box") %>% 
  layout(boxmode = "group", 
         xaxis = list(title = 'Season Year'),
         yaxis = list(title = "Defensive Rebounds"))
```

For some variables, we can only get average data for a team...
7. Isolation data
```{r}
predict_df %>% 
  ggplot(aes(x = season_year, y = poss_iso, color = play_off_team)) + 
  geom_point(alpha = .6) 

```


8. Passes made
No obvious pattern
```{r}
predict_df %>% 
  ggplot(aes(x = season_year, y = passes_made, color = play_off_team)) + 
  geom_point(alpha = .6) 
```

9. Pick and Roll Possession
No obvious pattern
```{r}
predict_df %>% 
  ggplot(aes(x = season_year, y = poss_pr, color = play_off_team)) + 
  geom_point()
```

Results of EDA
1. 哪些变量是季后赛球队和非季后赛球队有明显差异的<br>
According to above figures, we can conclude that teams which got into the play-off season each year have higher three pointer rate, three field goal attempt percentage and more defensive rebounds in each game.

2. 三分球出手率逐年上升，说明三分球越来越重要
And the overall trend of the three field goal attempt percentage has increased from 2012-13 season to 2020-21 season, which means that three point is a key to get into play-off season


### Have a look at response variable and explanatory variables

```{r,fig.asp=1, fig.width=10}
predict_df %>% 
  select(-fg3a_total, -fg3m_total, -play_off_team, -conf_rank) %>% 
  ggpairs(columns = 4:16)
```

The correlation between predictors are not very high, which is important for preventing collinearity.

### Modelling

We used backward elimination method to select the significant dependents. 

Firstly, put all the potential variables into the linear model, to see the regression results.

```{r,message=FALSE, warning=FALSE}
model1 = lm(data = predict_df, wins_revised ~ pts_avg + tov_avg + fg3_p + fg3_r + stl + blk + dreb + poss_trans + poss_iso + poss_pr + ast_avg + passes_made)
summary(model1)
anova(model1)
```

The adjusted R square for the full model is 0.5767 that is to say 57.67% of variances in the response variable can be explained by the predictors. 

Then, to get a better model with higher adjusted R square, we delete the less effective predictors with higher p-value, which is passes_made

```{r}
model2 = lm(data = predict_df, wins_revised ~ pts_avg + tov_avg + fg3_p + fg3_r + stl + blk + dreb + poss_trans + poss_iso + poss_pr + ast_avg)
summary(model2)
anova(model2)
```

The adjusted R square got improved to 0.5777. 57.77% of variances in the response variable can be explained by the predictors. 
Then delete the ast_avg which has the highest p-value among the variables left to see if the adjusted R square could be better.

```{r}
model3 = lm(data = predict_df, wins_revised ~ pts_avg + tov_avg + fg3_p + fg3_r + stl + blk + dreb + poss_trans + poss_iso + poss_pr)
summary(model3)
anova(model3)
```

The adjusted R square got decreased to 0.5768, so the ast_avg should be kept in the model. Model2 is the final model.

### Cross Validation
With respect to the above three models, we want to see which model has the best generalizability. So in this section, cross validation is used to compare candidate model
```{r}
predict_cv_df = 
  predict_df %>% 
  crossv_mc(100) %>% 
  mutate(train = map(train, as.tibble), 
         test = map(test, as.tibble))

predict_cv_df = 
  predict_cv_df %>% 
  mutate(model1 = map(train, ~lm(wins_revised ~ pts_avg + ast_avg + tov_avg + fg3_p + fg3_r + stl + blk + dreb + poss_trans + passes_made + poss_iso + poss_pr, data = .x)),  
         model2 = map(train, ~lm(wins_revised ~ pts_avg + ast_avg + tov_avg + fg3_p + fg3_r + stl + blk + dreb + poss_trans + poss_iso + poss_pr, data = .x)), 
         model3 = map(train, ~lm(wins_revised ~ pts_avg + tov_avg + fg3_p + fg3_r + stl + blk + dreb + poss_trans + poss_iso + poss_pr, data = .x))) %>% 
  mutate(rmse1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)), 
         rmse2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)), 
         rmse3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y)))
  

predict_cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(everything(), 
               names_to = "model", 
               names_prefix = "rmse", 
               values_to = "rmse") %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_boxplot()
  
```
The results rmse distribution of the three model are very similar to each other, which indicates similar level of generalizability. Therefore, we still use the model2 for the final model 


### Model diagnostic

1). to check the linearity between wins_revised and dependent variable.

```{r}
ggplot(data = predict_df, aes(x = fg3_r, y = wins_revised)) + geom_point() + geom_smooth(method = "lm", se = FALSE)


```


2). to check if the error term is normally distributed with mean 0.
```{r}
ggplot(data = model2, aes(x = model2$residuals)) + geom_histogram()
plot(model2, which = 1)
plot(model2, which = 2)
```

Condition 1 is met.

3). to check if the error term is constants, independent of the dependent variable.
```{r}
ggplot(data = model2, aes(x = model2$fitted.values, y = model2$residuals)) + geom_point() + geom_smooth(method = "lm", se = FALSE)
plot(model2, which = 3)
```

Condition 2 is met as we cannot see an obvious tendency of errors as wins_revised increase.

4) to check if there is any outliers or influencers in our data
```{r}
plot(model2, which = 4)
```
There is no influencers that exist in our data

### Interpretation of model coefficients



### Use the model to predict whether the Knicks can get in the play-off season in 2021-2022 

scrapping regular season data
```{r}
scrapping_data = function(url) {
  headers = headers = c(
  `Connection` = 'keep-alive',
  `Accept` = 'application/json, text/plain, */*',
  `x-nba-stats-token` = 'true',
  `X-NewRelic-ID` = 'VQECWF5UChAHUlNTBwgBVw==',
  `User-Agent` = 'Mozilla/5.0 (Macintosh; Intel Mac OS X 10_15_7) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/95.0.4638.69 Safari/537.36', 
  `x-nba-stats-origin` = 'stats',
  `Sec-Fetch-Site` = 'same-origin',
  `Sec-Fetch-Mode` = 'cors',
  `Referer` = 'https://stats.nba.com/players/leaguedashplayerbiostats/',
  `Accept-Encoding` = 'gzip, deflate, br',
  `Accept-Language` = 'en-US,en;q=0.9')
  response = GET(url, add_headers(headers))
  data = fromJSON(content(response, as = "text"))
  df = data.frame(data$resultSets$rowSet[[1]], stringAsFactors = FALSE)
  names(df) = tolower(data$resultSets$headers[[1]])
  return(df)
}

drop_last_column = function(df) {
  df = df %>% select(- names(df)[[length(names(df))]])
  return(df)
}




url_new = "https://stats.nba.com/stats/teamgamelogs?DateFrom=&DateTo=&GameSegment=&LastNGames=0&LeagueID=00&Location=&MeasureType=Base&Month=0&OpponentTeamID=0&Outcome=&PORound=0&PaceAdjust=N&PerMode=Totals&Period=0&PlusMinus=N&Rank=N&Season=2021-22&SeasonSegment=&SeasonType=Regular+Season&ShotClockRange=&VsConference=&VsDivision="

box_score_21_22 = 
  scrapping_data(url_new) %>% 
  drop_last_column()

transition_21_22 = scrapping_data("https://stats.nba.com/stats/synergyplaytypes?LeagueID=00&PerMode=PerGame&PlayType=Transition&PlayerOrTeam=T&SeasonType=Regular+Season&SeasonYear=2021-22&TypeGrouping=offensive") %>% 
  drop_last_column() %>% 
  mutate(season_year = "2021-22")

iso_21_22 = scrapping_data("https://stats.nba.com/stats/synergyplaytypes?LeagueID=00&PerMode=PerGame&PlayType=Isolation&PlayerOrTeam=T&SeasonType=Regular+Season&SeasonYear=2021-22&TypeGrouping=offensive") %>% drop_last_column()%>% 
  mutate(season_year = "2021-22")

prbh_21_22 = scrapping_data(("https://stats.nba.com/stats/synergyplaytypes?LeagueID=00&PerMode=PerGame&PlayType=PRBallHandler&PlayerOrTeam=T&SeasonType=Regular+Season&SeasonYear=2021-22&TypeGrouping=offensive")) %>% drop_last_column()%>% 
  mutate(season_year = "2021-22")

prrm_21_22 = scrapping_data("https://stats.nba.com/stats/synergyplaytypes?LeagueID=00&PerMode=PerGame&PlayType=PRRollman&PlayerOrTeam=T&SeasonType=Regular+Season&SeasonYear=2021-22&TypeGrouping=offensive") %>% drop_last_column()%>% 
  mutate(season_year = "2021-22")

defend_21_22 = scrapping_data("https://stats.nba.com/stats/leaguedashptstats?College=&Conference=&Country=&DateFrom=&DateTo=&Division=&DraftPick=&DraftYear=&GameScope=&GameSegment=&Height=&LastNGames=0&LeagueID=00&Location=&Month=0&OpponentTeamID=0&Outcome=&PORound=0&PerMode=PerGame&Period=0&PlayerExperience=&PlayerOrTeam=Team&PlayerPosition=&PtMeasureType=Defense&Season=2021-22&SeasonSegment=&SeasonType=Regular+Season&StarterBench=&TeamID=0&VsConference=&VsDivision=&Weight=") %>% 
  drop_last_column() %>% 
  mutate(season_year = "2021-22")

pass_21_22 = scrapping_data("https://stats.nba.com/stats/leaguedashptstats?College=&Conference=&Country=&DateFrom=&DateTo=&Division=&DraftPick=&DraftYear=&GameScope=&GameSegment=&Height=&LastNGames=0&LeagueID=00&Location=&Month=0&OpponentTeamID=0&Outcome=&PORound=0&PerMode=PerGame&Period=0&PlayerExperience=&PlayerOrTeam=Team&PlayerPosition=&PtMeasureType=Passing&Season=2021-22&SeasonSegment=&SeasonType=Regular+Season&StarterBench=&TeamID=0&VsConference=&VsDivision=&Weight=") %>% 
  drop_last_column() %>% 
  mutate(season_year = "2021-22")
  
```

```{r}
box_score_21_22 = 
  box_score_21_22 %>% 
  select(
    season_year, 
    team_abbreviation, 
    wl, 
    pts, 
    ast, 
    tov, 
    fgm, 
    fga, 
    fg3m, 
    fg3a
    ) %>%
  mutate(
    win = case_when(wl == "W" ~ 1, TRUE~0),
    game_num = 1,
    fg3a_p = round(as.numeric(fg3a)/as.numeric(fga), digits = 3),
    conference = case_when(
      team_abbreviation %in% c("UTA","PHX","LAC","DEN","DAL","LAL","POR","GSW","SAS","MEM","NOP","SAC","MIN","OKC","HOU","NOH","SEA","NOK","CHH")~"west",
      team_abbreviation %in% c("PHI","BKN","MIL","ATL","NYK","MIA","BOS","IND","WAS","CHI","TOR","CLE","ORL","DET","NJN","CHA")~"east") # divide into east and west conference
    ) %>% 
  group_by(season_year, team_abbreviation, conference) %>% 
  summarise(
    wins = sum(win), 
    games = sum(game_num), 
    pts_avg = round(mean(as.numeric(pts)), digits = 1), 
    ast_avg = round(mean(as.numeric(ast)), digits = 1),
    tov_avg = round(mean(as.numeric(tov)), digits = 1),
    fgm_total = sum(as.numeric(fgm)), 
    fga_total = sum(as.numeric(fga)), 
    fg3m_total = sum(as.numeric(fg3m)), 
    fg3a_total = sum(as.numeric(fg3a))
    ) %>% 
  relocate(season_year, team_abbreviation, conference, wins, everything()) %>% 
  arrange(desc(season_year),desc(wins))

box_score_21_22 = 
  box_score_21_22  %>% 
  mutate(fg3_p = fg3a_total/fga_total, fg3_r = fg3m_total/fg3a_total) %>%
  select(season_year, team_abbreviation, conference, pts_avg, ast_avg, tov_avg,fg3_p, fg3_r, fg3a_total, fg3m_total)
```

```{r}
trans_df = 
  transition_21_22 %>% 
  janitor::clean_names() %>% 
  select(season_year, team_abbreviation, poss) %>% 
  rename(poss_trans = poss)

pass_df = 
  pass_21_22 %>% 
  janitor::clean_names() %>% 
  select(season_year, team_abbreviation, passes_made)

isol_df = iso_21_22 %>% 
  janitor::clean_names() %>% 
  select(season_year, team_abbreviation, poss) %>%
  rename(poss_iso = poss)

prbh_df = 
  prbh_21_22 %>% 
  janitor::clean_names() %>% 
  select(season_year, team_abbreviation, poss) %>% 
  rename(poss_prb = poss)

prrm_df = 
  prrm_21_22 %>% 
  janitor::clean_names() %>% 
  select(season_year, team_abbreviation, poss) %>% 
  rename(poss_prr = poss)

defend_df = 
  defend_21_22 %>% 
  janitor::clean_names() %>% 
  select(season_year, team_abbreviation, stl, blk, dreb)
```

```{r}
new_season_df = 
  box_score_21_22 %>%
  left_join(defend_df, by = c("season_year","team_abbreviation")) %>% 
  left_join(prrm_df, by = c("season_year","team_abbreviation")) %>% 
  left_join(prbh_df, by = c("season_year","team_abbreviation")) %>%
  left_join(isol_df, by = c("season_year","team_abbreviation")) %>% 
  left_join(pass_df, by = c("season_year","team_abbreviation")) %>%
  left_join(trans_df, by = c("season_year","team_abbreviation")) %>% 
  drop_na(poss_trans, passes_made, poss_iso, poss_prb, poss_prr, stl, blk, dreb) %>% 
  mutate(
    poss_pr = as.numeric(poss_prr) + as.numeric(poss_prb)
  ) %>% 
  select(-poss_prr, -poss_prb) %>% 
  mutate(stl = as.numeric(stl), 
         blk = as.numeric(blk), 
         dreb = as.numeric(dreb), 
         poss_iso = as.numeric(poss_iso), 
         passes_made = as.numeric(passes_made), 
         poss_trans = as.numeric(poss_trans))
```


```{r}
rank = c(1:15)
prediction_21_22 = 
  modelr::add_predictions(new_season_df, model2) %>% select(conference, pred) %>% 
  filter(conference == "east") %>% 
  arrange(desc(pred)) 

prediction_21_22 %>% 
  knitr::kable()
```
Based on the boxscores of this season, we use model 2 to predict number of winnings for existing 30 teams. By arranging the predicted number of winnings, the Knicks is predicted to have 43.6 winnings this season and rank 8 in the season of 2021-22. According to this result, if the Knicks wants to secure a spot for playoff season, it has to improve its performance and tries to win more. 


Let's see what Knicks can do to improve its performance and rush into playoff season

```{r}
top8_east = 
  prediction_21_22 %>% 
  head(8) %>% 
  left_join(new_season_df, by = c("season_year", "team_abbreviation", "conference"))
```

Predicted Top 8 team average points earned each play
```{r}
top8_east %>% 
  ggplot(aes(x = reorder(team_abbreviation, pts_avg), y = pts_avg, fill = team_abbreviation)) + 
  geom_bar(stat = "identity") + 
  labs(
    x = "Team", 
    y = "Average Score per Game", 
    title = "Top 8 Team Average Score (East)"
  )
```

Difference in turnover
```{r}
top8_east %>% 
  ggplot(aes(x = reorder(team_abbreviation, tov_avg), y = tov_avg, fill = team_abbreviation)) + 
  geom_bar(stat="identity") + 
  labs(
    x = "Team", 
    y = "Average Turnover per Game", 
    title = "Top 8 Team Average Turnover (East)"
  )
```

Difference in fg3_r
```{r}
top8_east %>% 
  ggplot(aes(x = reorder(team_abbreviation, fg3_r), y = fg3_r, fill = team_abbreviation)) + 
  geom_bar(stat="identity") + 
  labs(
    x = "Team",
    y = "Three Pointer Rate",
    title = "Top 8 Team Three Pointer Rate (East)"
  )
```


Difference in steal
```{r}
top8_east %>% 
  ggplot(aes(x = reorder(team_abbreviation, stl), y = stl, fill = team_abbreviation)) + 
  geom_bar(stat="identity") + 
  labs(
    x = "Team", 
    y = "Average Steal per Game"
  )
```

Difference in block
```{r}
top8_east %>% 
  ggplot(aes(x = reorder(team_abbreviation, blk), y = blk, fill = team_abbreviation)) + 
  geom_bar(stat="identity") + 
  labs(x = "Team", 
       y = "Average Blocks per Game")
```

Diffrence in defense rebound
```{r}
top8_east %>% 
  ggplot(aes(x = reorder(team_abbreviation, dreb), y = dreb, fill = team_abbreviation)) + 
  geom_bar(stat="identity") + 
  labs(
    x = "Team", 
    y = "Average Defensive Rebound"
  )
```

Difference in transition
```{r}
top8_east %>% 
  ggplot(aes(x = reorder(team_abbreviation, poss_trans), y = poss_trans, fill = team_abbreviation)) + 
  geom_bar(stat="identity")+ 
  labs(x = "Team", 
       y = "Average Transition")
```

Difference in isolation
```{r}
top8_east %>% 
  ggplot(aes(x = reorder(team_abbreviation, poss_iso), y = poss_iso, fill = team_abbreviation)) + 
  geom_bar(stat="identity") + 
  labs(x = "Team", 
       y = "Average Isolation")
```

Difference in pick and roll
```{r}
top8_east %>% 
  ggplot(aes(x = reorder(team_abbreviation, poss_pr), y = poss_pr, fill = team_abbreviation)) + 
  geom_bar(stat="identity") + 
  labs(x = "Team", 
       y = "Average Pick and Roll")
```

Difference in average assistance
```{r}
top8_east %>% 
  ggplot(aes(x = reorder(team_abbreviation, ast_avg), y = ast_avg, fill = team_abbreviation)) + 
  geom_bar(stat="identity") + 
  labs(x = "Team", 
       y = "Average Assistance")
```
Based on model2, according to the existing data of New York Knicks in this 2021-22 season, we think  - TBC


### Zoom in - Three pointer shooting log
As three pointer is such a crutial parameter for NBA team to get into playoff season. We decide to look at Knicks' three pointer shooting data to offer more specific suggestions. In section, we will compare the overall performance of Knicks to league average, and then, draw the plots for some three pointer team leaders


Load and Tidy daya
```{r}
url = "https://stats.nba.com/stats/shotchartdetail?AheadBehind=&CFID=155&CFPARAMS=2021-22&ClutchTime=&Conference=&ContextFilter=&ContextMeasure=FGA&DateFrom=&DateTo=&Division=&EndPeriod=10&EndRange=28800&GROUP_ID=&GameEventID=&GameID=&GameSegment=&GroupID=&GroupMode=&GroupQuantity=5&LastNGames=0&LeagueID=00&Location=&Month=0&OnOff=&OpponentTeamID=0&Outcome=&PORound=0&Period=0&PlayerID=0&PlayerID1=&PlayerID2=&PlayerID3=&PlayerID4=&PlayerID5=&PlayerPosition=&PointDiff=&Position=&RangeType=0&RookieYear=&Season=2021-22&SeasonSegment=&SeasonType=Regular+Season&ShotClockRange=&StartPeriod=1&StartRange=0&StarterBench=&TeamID=1610612752&VsConference=&VsDivision=&VsPlayerID1=&VsPlayerID2=&VsPlayerID3=&VsPlayerID4=&VsPlayerID5=&VsTeamID="

shooting_log_df = 
  scrapping_data(url) %>% 
  drop_last_column()

#Alec Burks
url = "https://stats.nba.com/stats/shotchartdetail?AheadBehind=&CFID=33&CFPARAMS=2021-22&ClutchTime=&Conference=&ContextFilter=&ContextMeasure=FGA&DateFrom=&DateTo=&Division=&EndPeriod=10&EndRange=28800&GROUP_ID=&GameEventID=&GameID=&GameSegment=&GroupID=&GroupMode=&GroupQuantity=5&LastNGames=0&LeagueID=00&Location=&Month=0&OnOff=&OpponentTeamID=0&Outcome=&PORound=0&Period=0&PlayerID=202692&PlayerID1=&PlayerID2=&PlayerID3=&PlayerID4=&PlayerID5=&PlayerPosition=&PointDiff=&Position=&RangeType=0&RookieYear=&Season=2021-22&SeasonSegment=&SeasonType=Regular+Season&ShotClockRange=&StartPeriod=1&StartRange=0&StarterBench=&TeamID=0&VsConference=&VsDivision=&VsPlayerID1=&VsPlayerID2=&VsPlayerID3=&VsPlayerID4=&VsPlayerID5=&VsTeamID="

alec_log_df = 
  scrapping_data(url) %>% 
  drop_last_column()

#Kemba Walker
url = "https://stats.nba.com/stats/shotchartdetail?AheadBehind=&CFID=33&CFPARAMS=2021-22&ClutchTime=&Conference=&ContextFilter=&ContextMeasure=FGA&DateFrom=&DateTo=&Division=&EndPeriod=10&EndRange=28800&GROUP_ID=&GameEventID=&GameID=&GameSegment=&GroupID=&GroupMode=&GroupQuantity=5&LastNGames=0&LeagueID=00&Location=&Month=0&OnOff=&OpponentTeamID=0&Outcome=&PORound=0&Period=0&PlayerID=202689&PlayerID1=&PlayerID2=&PlayerID3=&PlayerID4=&PlayerID5=&PlayerPosition=&PointDiff=&Position=&RangeType=0&RookieYear=&Season=2021-22&SeasonSegment=&SeasonType=Regular+Season&ShotClockRange=&StartPeriod=1&StartRange=0&StarterBench=&TeamID=0&VsConference=&VsDivision=&VsPlayerID1=&VsPlayerID2=&VsPlayerID3=&VsPlayerID4=&VsPlayerID5=&VsTeamID="

walker_log_df = 
  scrapping_data(url) %>% 
  drop_last_column()

# Derrik Rose
url = "https://stats.nba.com/stats/shotchartdetail?AheadBehind=&CFID=33&CFPARAMS=2021-22&ClutchTime=&Conference=&ContextFilter=&ContextMeasure=FGA&DateFrom=&DateTo=&Division=&EndPeriod=10&EndRange=28800&GROUP_ID=&GameEventID=&GameID=&GameSegment=&GroupID=&GroupMode=&GroupQuantity=5&LastNGames=0&LeagueID=00&Location=&Month=0&OnOff=&OpponentTeamID=0&Outcome=&PORound=0&Period=0&PlayerID=201565&PlayerID1=&PlayerID2=&PlayerID3=&PlayerID4=&PlayerID5=&PlayerPosition=&PointDiff=&Position=&RangeType=0&RookieYear=&Season=2021-22&SeasonSegment=&SeasonType=Regular+Season&ShotClockRange=&StartPeriod=1&StartRange=0&StarterBench=&TeamID=0&VsConference=&VsDivision=&VsPlayerID1=&VsPlayerID2=&VsPlayerID3=&VsPlayerID4=&VsPlayerID5=&VsTeamID="

rose_log_df = 
  scrapping_data(url) %>% 
  drop_last_column()

scrapping_data_lavg = function(url) {
  headers = headers = c(
  `Connection` = 'keep-alive',
  `Accept` = 'application/json, text/plain, */*',
  `x-nba-stats-token` = 'true',
  `X-NewRelic-ID` = 'VQECWF5UChAHUlNTBwgBVw==',
  `User-Agent` = 'Mozilla/5.0 (Macintosh; Intel Mac OS X 10_15_7) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/95.0.4638.69 Safari/537.36', 
  `x-nba-stats-origin` = 'stats',
  `Sec-Fetch-Site` = 'same-origin',
  `Sec-Fetch-Mode` = 'cors',
  `Referer` = 'https://stats.nba.com/players/leaguedashplayerbiostats/',
  `Accept-Encoding` = 'gzip, deflate, br',
  `Accept-Language` = 'en-US,en;q=0.9')
  response = GET(url, add_headers(headers))
  data = fromJSON(content(response, as = "text"))
  df = data.frame(data$resultSets$rowSet[[2]], stringAsFactors = FALSE)
  names(df) = tolower(data$resultSets$headers[[2]])
  return(df)
}

league_avg_df = scrapping_data_lavg(url) %>% drop_last_column()


# some data tidy
width = 50
height = 94 / 2
key_height = 19
inner_key_width = 12
outer_key_width = 16
backboard_width = 6
backboard_offset = 4
neck_length = 0.5
hoop_radius = 0.75
hoop_center_y = backboard_offset + neck_length + hoop_radius
three_point_radius = 23.75
three_point_side_radius = 22
three_point_side_height = 14

shooting_log_df = 
  shooting_log_df %>% 
  mutate(loc_x = as.numeric(loc_x) / 10,
         loc_y = as.numeric(loc_y) / 10 + hoop_center_y, 
         shot_distance = as.numeric(as.character(shot_distance)),
         shot_made_numeric = as.numeric(shot_made_flag),
         shot_made_flag = factor(shot_made_flag, levels = c("1", "0"), labels = c("made", "missed")),
         shot_attempted_flag = as.numeric(as.character(shot_attempted_flag)),
         shot_value = ifelse(tolower(shot_type) == "3pt field goal", 3, 2),
         game_date = as.Date(game_date, format = "%Y%m%d")) %>% 
  filter(shot_type == "3PT Field Goal")

alec_log_df = 
  alec_log_df %>% 
  mutate(loc_x = as.numeric(loc_x) / 10,
         loc_y = as.numeric(loc_y) / 10 + hoop_center_y, 
         shot_distance = as.numeric(as.character(shot_distance)),
         shot_made_numeric = as.numeric(shot_made_flag),
         shot_made_flag = factor(shot_made_flag, levels = c("1", "0"), labels = c("made", "missed")),
         shot_attempted_flag = as.numeric(as.character(shot_attempted_flag)),
         shot_value = ifelse(tolower(shot_type) == "3pt field goal", 3, 2),
         game_date = as.Date(game_date, format = "%Y%m%d")) %>% 
  filter(shot_type == "3PT Field Goal")

walker_log_df = 
  walker_log_df %>% 
  mutate(loc_x = as.numeric(loc_x) / 10,
         loc_y = as.numeric(loc_y) / 10 + hoop_center_y, 
         shot_distance = as.numeric(as.character(shot_distance)),
         shot_made_numeric = as.numeric(shot_made_flag),
         shot_made_flag = factor(shot_made_flag, levels = c("1", "0"), labels = c("made", "missed")),
         shot_attempted_flag = as.numeric(as.character(shot_attempted_flag)),
         shot_value = ifelse(tolower(shot_type) == "3pt field goal", 3, 2),
         game_date = as.Date(game_date, format = "%Y%m%d")) %>% 
  filter(shot_type == "3PT Field Goal")

rose_log_df = 
  rose_log_df %>% 
  mutate(loc_x = as.numeric(loc_x) / 10,
         loc_y = as.numeric(loc_y) / 10 + hoop_center_y, 
         shot_distance = as.numeric(as.character(shot_distance)),
         shot_made_numeric = as.numeric(shot_made_flag),
         shot_made_flag = factor(shot_made_flag, levels = c("1", "0"), labels = c("made", "missed")),
         shot_attempted_flag = as.numeric(as.character(shot_attempted_flag)),
         shot_value = ifelse(tolower(shot_type) == "3pt field goal", 3, 2),
         game_date = as.Date(game_date, format = "%Y%m%d")) %>% 
  filter(shot_type == "3PT Field Goal")


league_avg_df = 
  league_avg_df %>% 
  mutate(fga = as.numeric(as.character(fga)),
                           fgm = as.numeric(as.character(fgm)),
                           fg_pct = as.numeric(as.character(fg_pct)),
                           shot_value = ifelse(shot_zone_basic %in% c("Above the Break 3", "Backcourt", "Left Corner 3", "Right Corner 3"), 3, 2))
```


Draw half of NBA court - ballr package<br>
https://github.com/toddwschneider/ballr
```{r}
circle_points = function(center = c(0, 0), radius = 1, npoints = 360) {
  angles = seq(0, 2 * pi, length.out = npoints)
  return(data_frame(x = center[1] + radius * cos(angles),
                    y = center[2] + radius * sin(angles)))
}



court_themes = list(
  light = list(
    court = 'floralwhite',
    lines = '#999999',
    text = '#222222',
    made = '#00bfc4',
    missed = '#f8766d',
    hex_border_size = 1,
    hex_border_color = "#000000"
  ),
  dark = list(
    court = '#000004',
    lines = '#999999',
    text = '#f0f0f0',
    made = '#00bfc4',
    missed = '#f8766d',
    hex_border_size = 0,
    hex_border_color = "#000000"
  )
)


plot_court = function(court_theme = court_themes$light, use_short_three = FALSE) {
  if (use_short_three) {
    three_point_radius = 22
    three_point_side_height = 0
  }
  
  court_points = data_frame(
    x = c(width / 2, width / 2, -width / 2, -width / 2, width / 2),
    y = c(height, 0, 0, height, height),
    desc = "perimeter"
  )
  
  court_points = bind_rows(court_points , data_frame(
    x = c(outer_key_width / 2, outer_key_width / 2, -outer_key_width / 2, -outer_key_width / 2),
    y = c(0, key_height, key_height, 0),
    desc = "outer_key"
  ))
  
  court_points = bind_rows(court_points , data_frame(
    x = c(-backboard_width / 2, backboard_width / 2),
    y = c(backboard_offset, backboard_offset),
    desc = "backboard"
  ))
  
  court_points = bind_rows(court_points , data_frame(
    x = c(0, 0), y = c(backboard_offset, backboard_offset + neck_length), desc = "neck"
  ))
  
  foul_circle = circle_points(center = c(0, key_height), radius = inner_key_width / 2)
  
  foul_circle_top = filter(foul_circle, y > key_height) %>%
    mutate(desc = "foul_circle_top")
  
  foul_circle_bottom = filter(foul_circle, y < key_height) %>%
    mutate(
      angle = atan((y - key_height) / x) * 180 / pi,
      angle_group = floor((angle - 5.625) / 11.25),
      desc = paste0("foul_circle_bottom_", angle_group)
    ) %>%
    filter(angle_group %% 2 == 0) %>%
    select(x, y, desc)
  
  hoop = circle_points(center = c(0, hoop_center_y), radius = hoop_radius) %>%
    mutate(desc = "hoop")
  
  restricted = circle_points(center = c(0, hoop_center_y), radius = 4) %>%
    filter(y >= hoop_center_y) %>%
    mutate(desc = "restricted")
  
  three_point_circle = circle_points(center = c(0, hoop_center_y), radius = three_point_radius) %>%
    filter(y >= three_point_side_height, y >= hoop_center_y)
  
  three_point_line = data_frame(
    x = c(three_point_side_radius, three_point_side_radius, three_point_circle$x, -three_point_side_radius, -three_point_side_radius),
    y = c(0, three_point_side_height, three_point_circle$y, three_point_side_height, 0),
    desc = "three_point_line"
  )
  
  court_points = bind_rows(
    court_points,
    foul_circle_top,
    foul_circle_bottom,
    hoop,
    restricted,
    three_point_line
  )
  
  
  court_points <- court_points
  
  ggplot() +
    geom_path(
      data = court_points,
      aes(x = x, y = y, group = desc),
      color = court_theme$lines
    ) +
    coord_fixed(ylim = c(0, 45), xlim = c(-25, 25)) +
    theme_minimal(base_size = 22) +
    theme(
      text = element_text(color = court_theme$text),
      plot.background = element_rect(fill = 'floralwhite', color = 'floralwhite'),
      panel.background = element_rect(fill = court_theme$court, color = court_theme$court),
      panel.grid = element_blank(),
      panel.border = element_blank(),
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      legend.background = element_rect(fill = court_theme$court, color = court_theme$court),
      legend.margin = margin(-1, 0, 0, 0, unit = "lines"),
      legend.position = "bottom",
      legend.key = element_blank(),
      legend.text = element_text(size = rel(1.0))
    )
}
```

take shooting log data and map into hexagons - blog<br>
https://www.owenlhjphillips.com/new-blog/2020/6/25/how-to-make-nba-shots-charts-in-r
```{r}
hex_bounds <- function(x, binwidth) {
  c(
    plyr::round_any(min(x), binwidth, floor) - 1e-6,
    plyr::round_any(max(x), binwidth, ceiling) + 1e-6
  )
}

calculate_hex_coords = function(shots, binwidths) {
  xbnds = hex_bounds(shots$loc_x, binwidths[1])
  xbins = diff(xbnds) / binwidths[1]
  ybnds = hex_bounds(shots$loc_y, binwidths[2])
  ybins = diff(ybnds) / binwidths[2]
  
  hb = hexbin(
    x = shots$loc_x,
    y = shots$loc_y,
    xbins = xbins,
    xbnds = xbnds,
    ybnds = ybnds,
    shape = ybins / xbins,
    IDs = TRUE
  )
  
  shots = mutate(shots, hexbin_id = hb@cID)
  
  hexbin_stats = shots %>%
    group_by(hexbin_id) %>%
    summarize(
      hex_attempts = n(),
      hex_pct = mean(shot_made_numeric),
      hex_points_scored = sum(shot_made_numeric * shot_value),
      hex_points_per_shot = mean(shot_made_numeric * shot_value)
    ) 
  
  hexbin_ids_to_zones = shots %>%
    group_by(hexbin_id, shot_zone_range, shot_zone_area) %>%
    summarize(attempts = n()) %>%
    ungroup() %>%
    arrange(hexbin_id, desc(attempts)) %>%
    group_by(hexbin_id) %>%
    filter(row_number() == 1) %>%
    select(hexbin_id, shot_zone_range, shot_zone_area)
  
  hexbin_stats = inner_join(hexbin_stats, hexbin_ids_to_zones, by = "hexbin_id")
  
  # from hexbin package, see: https://github.com/edzer/hexbin
  sx = hb@xbins / diff(hb@xbnds)
  sy = (hb@xbins * hb@shape) / diff(hb@ybnds)
  dx = 1 / (2 * sx)
  dy = 1 / (2 * sqrt(3) * sy)
  origin_coords = hexcoords(dx, dy)
  
  hex_centers = hcell2xy(hb)
  
  hexbin_coords = bind_rows(lapply(1:hb@ncells, function(i) {
    data.frame(
      x = origin_coords$x + hex_centers$x[i],
      y = origin_coords$y + hex_centers$y[i],
      center_x = hex_centers$x[i],
      center_y = hex_centers$y[i],
      hexbin_id = hb@cell[i]
    )
  }))
  
  inner_join(hexbin_coords, hexbin_stats, by = "hexbin_id")
}


calculate_hexbins_from_shots = function(shots, league_averages, binwidths, min_radius_factor, fg_diff_limits, fg_pct_limits, pps_limits) {
  if (nrow(shots) == 0) {
    return(list())
  }
  
  grouped_shots = group_by(shots, shot_zone_range, shot_zone_area)
  
  zone_stats = grouped_shots %>%
    summarize(
      zone_attempts = n(),
      zone_pct = mean(shot_made_numeric),
      zone_points_scored = sum(shot_made_numeric * shot_value),
      zone_points_per_shot = mean(shot_made_numeric * shot_value)
    )
  
  league_zone_stats = league_averages %>%
    group_by(shot_zone_range, shot_zone_area) %>%
    summarize(league_pct = sum(fgm) / sum(fga))
  
  hex_data = calculate_hex_coords(shots, binwidths = binwidths)
  
  join_keys = c("shot_zone_area", "shot_zone_range")
  
  hex_data = hex_data %>%
    inner_join(zone_stats, by = join_keys) %>%
    inner_join(league_zone_stats, by = join_keys)
  
  max_hex_attempts = max(hex_data$hex_attempts)
  
  
  hex_data = mutate(hex_data,
                    radius_factor = min_radius_factor + (1 - min_radius_factor) * log(hex_attempts + 1) / log(max_hex_attempts + 1),
                    adj_x = center_x + radius_factor * (x - center_x),
                    adj_y = center_y + radius_factor * (y - center_y),
                    league_avg_diff = pmin(pmax(zone_pct - league_pct, fg_diff_limits[1]), fg_diff_limits[2]),
                    bounded_fg_pct = pmin(pmax(zone_pct, fg_pct_limits[1]), fg_pct_limits[2]),
                    bounded_points_per_shot = pmin(pmax(zone_points_per_shot, pps_limits[1]), pps_limits[2]))
  
  list(hex_data = hex_data, fg_diff_limits = fg_diff_limits, fg_pct_limits = fg_pct_limits, pps_limits = pps_limits)
  
}


```

```{r}
hex_data = calculate_hexbins_from_shots(shooting_log_df, league_avg_df,binwidths = c(1.5,1.5), min_radius_factor = .25, fg_diff_limits = c(-0.15, 0.15), fg_pct_limits = c(0.2, 0.7), pps_limits = c(0.5, 1.5))  
  
df = hex_data
  
df = as.data.frame(df[1])
  
#df$season <- seasons
#df$person_id <- id
  
  
names(df) <- sub(".*\\.", "", names(df))

alec_hex_data = calculate_hexbins_from_shots(alec_log_df, league_avg_df,binwidths = c(1.5,1.5), min_radius_factor = .25, fg_diff_limits = c(-0.15, 0.15), fg_pct_limits = c(0.2, 0.7), pps_limits = c(0.5, 1.5)) 

alec_df = alec_hex_data
alec_df = as.data.frame(alec_df[1])
#alec_df$season <- seasons
#alec_df$person_id <- id

walker_hex_data = calculate_hexbins_from_shots(walker_log_df, league_avg_df,binwidths = c(1.5,1.5), min_radius_factor = .25, fg_diff_limits = c(-0.15, 0.15), fg_pct_limits = c(0.2, 0.7), pps_limits = c(0.5, 1.5)) 

walker_df = walker_hex_data
walker_df = as.data.frame(walker_df[1])


rose_hex_data = calculate_hexbins_from_shots(rose_log_df, league_avg_df,binwidths = c(1.5,1.5), min_radius_factor = .25, fg_diff_limits = c(-0.15, 0.15), fg_pct_limits = c(0.2, 0.7), pps_limits = c(0.5, 1.5)) 

rose_df = rose_hex_data
rose_df = as.data.frame(rose_df[1])
```

adjust some aesthetics - blog<br>
https://www.owenlhjphillips.com/new-blog/2020/6/25/how-to-make-nba-shots-charts-in-r

According to this hex plot, in the 2021-2022 regular season, The Knicks has a better performance in three-point field goal at both of the wing area compared to league average. And it has a equal performance with the league average at the head of the key area. However, the Knicks performs worse at the both corner area compared to the league average. To be more specific, the three pointer percentage at right wing is 6% higher than the league average. At left wing, the three pointer percentage is 3% higher than the league average. On the other hand, the team's three pointer percentage is 6% and 3% lower than the league average in the right and left corners respectively. Therefore, the Knicks should deploy more three field goal tactics at left and right wing areas. And the shooting ability at corner area should be further strengthened through training. 
```{r}
library(prismatic)
library(extrafont)
library(cowplot)

p = plot_court(court_themes$light) +
  geom_polygon(
    data = df,
    aes(
      x = adj_x,
      y = adj_y,
      group = hexbin_id, 
      fill = league_avg_diff, 
      color = after_scale(clr_darken(fill, .333))),
    size = .25) + 
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  scale_fill_distiller(direction = -1, 
                       palette = "PuOr", 
                       limits = c(-.15, .15), 
                       breaks = seq(-.15, .15, .03),
                       labels = c("-15%", "-12%", "-9%", "-6%", "-3%", "0%", "+3%", "+6%", "+9%", "+12%", "+15%"),
                       "3FG Percentage Points vs. League Average") +
  guides(fill = guide_legend(
    label.position = 'bottom', 
    title.position = 'top', 
    keywidth = .45,
    keyheight = .15, 
    default.unit = "inch", 
    title.hjust = .5,
    title.vjust = 0,
    label.vjust = 3,
    nrow = 1))  +
  theme(legend.spacing.x = unit(0, 'cm'), 
        legend.title = element_text(size = 9), 
        legend.text = element_text(size = 8), 
        legend.margin = margin(-10,0,-1,0),
        legend.position = 'bottom',
        legend.box.margin = margin(-30,0,15,0), 
        plot.title = element_text(hjust = 0.5, vjust = -1, size = 15),
        plot.subtitle = element_text(hjust = 0.5, size = 8, vjust = -.5), 
        plot.caption = element_text(face = "italic", size = 8), 
        plot.margin = margin(0, -5, 0, -5, "cm")) +
  labs(title = "New York Knicks - Three Point",
       subtitle = "2021-22 Regular Season")

ggdraw(p) + 
  theme(plot.background = element_rect(fill="floralwhite", color = NA))
```

Alec shooting visualization

```{r}
alec_p = 
  plot_court(court_themes$light) +
  geom_polygon(
    data = alec_df,
    aes(
      x = hex_data.adj_x,
      y = hex_data.adj_y,
      group = hex_data.hexbin_id, 
      fill = hex_data.league_avg_diff, 
      color = after_scale(clr_darken(fill, .333))),
    size = .25) + 
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  scale_fill_distiller(direction = -1, 
                       palette = "PuOr", 
                       limits = c(-.15, .15), 
                       breaks = seq(-.15, .15, .03),
                       labels = c("-15%", "-12%", "-9%", "-6%", "-3%", "0%", "+3%", "+6%", "+9%", "+12%", "+15%"),
                       "3FG Percentage Points vs. League Average") +
  guides(fill = guide_legend(
    label.position = 'bottom', 
    title.position = 'top', 
    keywidth = .45,
    keyheight = .15, 
    default.unit = "inch", 
    title.hjust = .5,
    title.vjust = 0,
    label.vjust = 3,
    nrow = 1))  +
  theme(legend.spacing.x = unit(0, 'cm'), 
        legend.title = element_text(size = 9), 
        legend.text = element_text(size = 8), 
        legend.margin = margin(-10,0,-1,0),
        legend.position = 'bottom',
        legend.box.margin = margin(-30,0,15,0), 
        plot.title = element_text(hjust = 0.5, vjust = -1, size = 15),
        plot.subtitle = element_text(hjust = 0.5, size = 8, vjust = -.5), 
        plot.caption = element_text(face = "italic", size = 8), 
        plot.margin = margin(0, -5, 0, -5, "cm")) +
  labs(title = "Alec Burks - Three Point",
       subtitle = "2021-22 Regular Season")

ggdraw(alec_p) + 
  theme(plot.background = element_rect(fill="floralwhite", color = NA))
```

Kaemba Walker shooting visualization
```{r}
walker_p = 
  plot_court(court_themes$light) +
  geom_polygon(
    data = walker_df,
    aes(
      x = hex_data.adj_x,
      y = hex_data.adj_y,
      group = hex_data.hexbin_id, 
      fill = hex_data.league_avg_diff, 
      color = after_scale(clr_darken(fill, .333))),
    size = .25) + 
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  scale_fill_distiller(direction = -1, 
                       palette = "PuOr", 
                       limits = c(-.15, .15), 
                       breaks = seq(-.15, .15, .03),
                       labels = c("-15%", "-12%", "-9%", "-6%", "-3%", "0%", "+3%", "+6%", "+9%", "+12%", "+15%"),
                       "3FG Percentage Points vs. League Average") +
  guides(fill = guide_legend(
    label.position = 'bottom', 
    title.position = 'top', 
    keywidth = .45,
    keyheight = .15, 
    default.unit = "inch", 
    title.hjust = .5,
    title.vjust = 0,
    label.vjust = 3,
    nrow = 1))  +
  theme(legend.spacing.x = unit(0, 'cm'), 
        legend.title = element_text(size = 9), 
        legend.text = element_text(size = 8), 
        legend.margin = margin(-10,0,-1,0),
        legend.position = 'bottom',
        legend.box.margin = margin(-30,0,15,0), 
        plot.title = element_text(hjust = 0.5, vjust = -1, size = 15),
        plot.subtitle = element_text(hjust = 0.5, size = 8, vjust = -.5), 
        plot.caption = element_text(face = "italic", size = 8), 
        plot.margin = margin(0, -5, 0, -5, "cm")) +
  labs(title = "Kemba Walker - Three Point",
       subtitle = "2021-22 Regular Season")

ggdraw(walker_p) + 
  theme(plot.background = element_rect(fill="floralwhite", color = NA))
```

Derrick Rose shooting visualization
```{r}
rose_p = 
  plot_court(court_themes$light) +
  geom_polygon(
    data = rose_df,
    aes(
      x = hex_data.adj_x,
      y = hex_data.adj_y,
      group = hex_data.hexbin_id, 
      fill = hex_data.league_avg_diff, 
      color = after_scale(clr_darken(fill, .333))),
    size = .25) + 
  scale_x_continuous(limits = c(-27.5, 27.5)) + 
  scale_y_continuous(limits = c(0, 45)) +
  scale_fill_distiller(direction = -1, 
                       palette = "PuOr", 
                       limits = c(-.15, .15), 
                       breaks = seq(-.15, .15, .03),
                       labels = c("-15%", "-12%", "-9%", "-6%", "-3%", "0%", "+3%", "+6%", "+9%", "+12%", "+15%"),
                       "3FG Percentage Points vs. League Average") +
  guides(fill = guide_legend(
    label.position = 'bottom', 
    title.position = 'top', 
    keywidth = .45,
    keyheight = .15, 
    default.unit = "inch", 
    title.hjust = .5,
    title.vjust = 0,
    label.vjust = 3,
    nrow = 1))  +
  theme(legend.spacing.x = unit(0, 'cm'), 
        legend.title = element_text(size = 9), 
        legend.text = element_text(size = 8), 
        legend.margin = margin(-10,0,-1,0),
        legend.position = 'bottom',
        legend.box.margin = margin(-30,0,15,0), 
        plot.title = element_text(hjust = 0.5, vjust = -1, size = 15),
        plot.subtitle = element_text(hjust = 0.5, size = 8, vjust = -.5), 
        plot.caption = element_text(face = "italic", size = 8), 
        plot.margin = margin(0, -5, 0, -5, "cm")) +
  labs(title = "Derrick Rose - Three Point",
       subtitle = "2021-22 Regular Season")

ggdraw(rose_p) + 
  theme(plot.background = element_rect(fill="floralwhite", color = NA))
```

Alec Burks, Kemba Walker and Derrick Rose are the three point leader in Knicks. However, in the 2021-2022 season, none of them performs better than the league average in both of the corner area. 

### Conclusion









