---
title: "MLR_nwins"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(GGally)
library(modelr)
library(hexbin)
library(jsonlite)
library(httr)
library(patchwork)
library(plotly)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


```{r read boxscore dataset, include = FALSE, message=FALSE, warning=FALSE}
box_score_all = read_csv("./data2/box_score_all.csv") %>% 
  janitor::clean_names() %>% 
  select(-contains("rank"))
```


```{r other datasets, include=FALSE}
box_score_all = read_csv("./data2/box_score_all.csv") %>% 
  janitor::clean_names() %>% 
  select(-contains("rank"))

pass_df = 
  read_csv("./data2/pass_df.csv") %>% 
  select(season_year, team_abbreviation, passes_made)

isol_df = 
  read_csv("./data2/isol_df.csv") %>% 
  select(season_year, team_abbreviation, poss) %>% 
  rename(poss_iso = poss)

prbh_df = 
  read_csv("./data2/prbh_df.csv") %>% 
  select(season_year, team_abbreviation, poss) %>% 
  rename(poss_prb = poss)

prrm_df = 
  read_csv("./data2/prrm_df.csv") %>% 
  select(season_year, team_abbreviation, poss) %>% 
  rename(poss_prr = poss)

defend_df = 
  read_csv("./data2/defensive_impact_df.csv") %>% 
  select(season_year, team_abbreviation, stl, blk, dreb)

trans_df = 
  read_csv("./data2/transition_df.csv") %>% 
  select(season_year, team_abbreviation, poss) %>% 
  rename(poss_trans = poss)
```


```{r wrangling 1,message=FALSE, warning=FALSE}
avg_df = 
  box_score_all %>% 
  select(season_year, team_abbreviation, wl, pts, ast, tov, fgm, fga, fg3m, fg3a) %>%
  mutate(
    win = case_when(wl == "W" ~ 1, TRUE~0),
    game_num = 1,
    fg3a_p = round(fg3a/fga, digits = 3),
    team_abbreviation = str_replace(team_abbreviation, "NOH", "NOP"), 
    team_abbreviation = str_replace(team_abbreviation, "NJN", "BKN"),
    conference = case_when(
      team_abbreviation %in% c("UTA","PHX","LAC","DEN","DAL","LAL","POR","GSW","SAS","MEM","NOP","SAC","MIN","OKC","HOU","SEA","NOK","CHH")~"west",
      team_abbreviation %in% c("PHI","BKN","MIL","ATL","NYK","MIA","BOS","IND","WAS","CHI","TOR","CLE","ORL","DET","CHA")~"east") # divide into east and west conference
    ) %>% 
  group_by(season_year, team_abbreviation, conference) %>% 
  summarise(
    wins = sum(win), 
    games = sum(game_num), 
    games_should = 82, 
    pts_avg = round(mean(pts), digits = 1), 
    ast_avg = round(mean(ast), digits = 1),
    tov_avg = round(mean(tov), digits = 1),
    fgm_total = sum(fgm), 
    fga_total = sum(fga), 
    fg3m_total = sum(fg3m), 
    fg3a_total = sum(fg3a)
    ) %>% 
  mutate(wins_revised = round(wins/games*games_should,0)) %>% # due to labor negotiation in 2011-12, COVID-19.
  relocate(season_year, team_abbreviation, conference, wins, wins_revised, everything()) %>% 
  arrange(desc(season_year),desc(wins)) %>% 
  mutate(fg3_p = fg3a_total/fga_total, fg3_r = fg3m_total/fg3a_total) %>% 
  group_by(season_year,conference) %>% 
  mutate(
    conf_rank = row_number(),
    play_off_team = case_when(
           conf_rank <= 8 ~ "playoff", 
           conf_rank > 8 ~ "non-playoff"
         ), 
         play_off_team = fct_relevel(play_off_team, c("playoff", "non-playoff")))
```

```{r wrangling 2,message=FALSE, warning=FALSE}
predict_df = 
  avg_df %>%
  left_join(defend_df, by = c("season_year","team_abbreviation")) %>% 
  left_join(prrm_df, by = c("season_year","team_abbreviation")) %>% 
  left_join(prbh_df, by = c("season_year","team_abbreviation")) %>%
  left_join(isol_df, by = c("season_year","team_abbreviation")) %>% 
  left_join(pass_df, by = c("season_year","team_abbreviation")) %>%
  left_join(trans_df, by = c("season_year","team_abbreviation")) %>% 
  drop_na(poss_trans, passes_made, poss_iso, poss_prb, poss_prr, stl, blk, dreb) %>% 
  mutate(
    poss_pr = poss_prr + poss_prb
  ) %>% 
  select(-poss_prr, -poss_prb, -wins, -games, -games_should, -fgm_total, -fga_total)
```


## Regression Exploration

The resulting data frame of predict_df contains `r nrow(predict_df)` observations and `r ncol(predict_df)` variables. Each observations represent a team's average data in one regular season. Dependent variable is the number of wins by team and season, denoted by wins_revised. Independent variables are selected from both offensive aspect and defensive part.

The typical attributes of "small ball era" is more three points shooting and quicker speed. So we select the following variables representing offensive level of a team:
* fg3_p: proportion of three points shooting
* fg3_r: three points shooting rate
* pts_avg: average points per game
* tov_avg: average number of turnovers per game
* ast_avg: average number of assists per game
* poss_trans: average number of transitions
* passes_made: average number of passes per game
* poss_iso: average number of isolations per game 
* poss_pr: average number of pick and rolls

As for the defensive level, variables include:

* stl: average steals per game
* blk: average blocks per game
* dreb: average defensive rebounds per game

### Correlation Matrix 


